### 2019-08-22 maciek.tex
Omega(kl)

  Now, we formally define $c(x^{(i)})$, and the ordering of nodes in the initial configuration.
  Consider a set of nodes from an initial configuration of a cluster $C$ (where $C \neq A$).
  By $v^C_1$ we label the first node of a cluster $C$ that appears in the sequence $\langle x^{(i)}\rangle$.
  At this point, we fix an arbitrary other node of $C$ and we label it $v^C_0$, and we set $c(v^C_i) = v^C_0$ for all $i$.
  For the following $k-2$ nodes of the cluster $C$, we label them $v^C_2, v^C_3, \ldots$ in the order of appearance in the sequence $\langle x^{(i)}\rangle$.
  %For a node $v^C_p = x^{(j)}$, we set $y^{(j)} = v^C_0$.
  If some nodes of $C$ might never appear in the sequence $\langle x^{(i)}\rangle$ %(e.g. DET might terminate prematurely or might reside in a configuration with components split)
  , we number them arbitrarily, with the restriction that the nodes that do appear in the sequence have smaller number than the ones that do not \maciek{This should not happen at all for component-respecting DET, though}

  Now, we claim that given the input $I_1I_2$, every component-respecting DET 
  % (that does not terminate prematurely and never resides in a configuration with components split)
  must produce a sequence $\langle x^{(i)}\rangle$ of length $L = k\cdot \ell - (k-1) - 2 - (\ell-1) - 1$.
  Consider a request $(x^{(i)}, c(x^{(i)}))$.
  If in this configuration at least one singleton component is present (other than the components of $(x^{(i)}, c(x^{(i)}))$), then serving this request is possible (i.e., the perfect partition exists), and a singleton node appears as $x^{(i+1)}$, and the sequence continues.
  Otherwise, as we have a component $a_1, \ldots, a_{k-1}$, no perfect partition exists.

  Hence, the length of a sequence $\langle x^{(i)}\rangle$ depends on the number of singleton components.
  Before the arrival of the first request from $I_2$, the number of singleton components is $L + (\ell-1) + 1$, and after serving the last request, the number of singleton components is $1$.
  %Every node $x^{(i)}$ must be a singleton component, otherwise DET resides in a configuration with components split (and such DETs either leave such configuration eventually or issue an infinite cost).
  After each request, we join this singleton component with another component.
  This join decreases the number of singleton components by one or by two: if this is the join of two singletons $v^C_0, v^C_1$ (there are $\ell-1$ such joins: for all clusters but $A$), then the number of singletons decrease by $2$, and it decreases by $1$ otherwise.
  We conclude that the number of requests $\langle x^{(i)}\rangle$ to decrease the number of singletons to $1$ is $L$.

@@

  To this end, we inspect the sequences $v^{C}_i$ for each cluster, and select the cluster $C'$ whose node $v^{C'}_{k-2}$, i.e., the penultimate node appear last in the sequence $\langle x^{(i)}\rangle$, and end the sequence $I_2'$ just before its appearance.
  Then, we set $d^{(1)} = v^{C'}_{k-2}$, $d^{(2)} = v^{C'}_{k-1}$.
  Such choice guarantees that requests from $I_2'$ are free for OPT.
  Furthermore, the number of requests of $I_2'$ is at least $|I_2| - \ell - 1$: as $D$ is the last cluster to remain with two singleton clusters, all other $\ell-1$ clusters have at most $1$ singleton cluster.

@@

>>>>

  Now, we formally define $c(x^{(i)})$, and the ordering of nodes in the initial configuration.
  Consider a set of nodes from an initial configuration of a cluster $C$ (where $C \neq A$).
  By $v^C_1$ we label the first node of a cluster $C$ that appears in the sequence $\langle x^{(i)}\rangle$.
  At this point, we fix an arbitrary other node of $C$ and we label it $v^C_0$, and we set $c(v^C_i) = v^C_0$ for all $i$.
  For the following $k-2$ nodes of the cluster $C$, we label them $v^C_2, v^C_3, \ldots$ in the order of appearance in the sequence $\langle x^{(i)}\rangle$.
  %For a node $v^C_p = x^{(j)}$, we set $y^{(j)} = v^C_0$.
  If some nodes of $C$ never appear in the sequence $\langle x^{(i)}\rangle$ %(e.g. DET might terminate prematurely or might reside in a configuration with components split)
  , we number them arbitrarily, with the restriction that the nodes that do appear in the sequence have smaller number than the ones that do not \maciek{This should not happen at all for component-respecting DET, though}

  Now, we claim that given the input $I_1I_2$, every component-respecting DET 
  % (that does not terminate prematurely and never resides in a configuration with components split)
  must produce a sequence $\langle x^{(i)}\rangle$ of length $L = k\cdot \ell - (k-1) - 2 - (\ell-1) - 1$.
  Consider a request $(x^{(i)}, c(x^{(i)}))$.
  If in this configuration at least one singleton component is present (other than the components of $(x^{(i)}, c(x^{(i)}))$), then serving this request is possible (i.e., the perfect partition exists), and hence a singleton node appears as $x^{(i+1)}$ and the sequence continues.
  Otherwise, no perfect partition exists, as we have a component $\{a_1, \ldots, a_{k-1}\}$ of size $k-1$.

  Hence, the length of a sequence $\langle x^{(i)}\rangle$ is closely related to the number of singleton components.
  Before the arrival of the first request from $I_2$, the number of singleton components is $L + (\ell-1) + 1$, and after serving the last request, the number of singleton components is $1$.
  %Every node $x^{(i)}$ must be a singleton component, otherwise DET resides in a configuration with components split (and such DETs either leave such configuration eventually or issue an infinite cost).
  After each request, we join this singleton component with another component.
  This join decreases the number of singleton components by either $1$ or $2$: if we join two singletons $\{v^C_0\}, \{v^C_1\}$ (there are $\ell-1$ such joins: for all clusters but $A$), then the number of singletons decrease by $2$, and it decreases by $1$ otherwise.
  We conclude that the number of requests $\langle x^{(i)}\rangle$ to decrease the number of singletons to $1$ is $L$.

@@

  To this end, we inspect the sequences $v^{C}_i$ for each cluster, and select the cluster $C'$ whose node $v^{C'}_{k-2}$, i.e., the penultimate node appears last in the sequence $\langle x^{(i)}\rangle$, and we end the sequence $I_2'$ just before its appearance.
  Then, we set $d^{(1)} = v^{C'}_{k-2}$, $d^{(2)} = v^{C'}_{k-1}$.
  Such choice guarantees that requests from $I_2'$ are free for OPT.
  Furthermore, the number of requests of $I_2'$ is at least $|I_2| - \ell - 1$: as $D$ is the last cluster to remain with two singleton clusters, all other $\ell-1$ clusters have at most $1$ singleton cluster.

@@

  \maciek{ToDo: check all off-by-one errors}
  \maciek{ToDo: check if the existence of $b_1$ was considered in all calculations}
